---
title: "Introduction to efaTrail"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to efaTrail}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

## The problem

Developing a multidimensional instrument (a questionnaire with several
sub-scales, or "constructs") usually means running exploratory factor
analysis (EFA) separately for each construct, removing weak items one at a
time, re-running, and writing up every iteration -- often as a long
supplementary appendix.

Existing R and Python tools (`psych`, `EFAtools`, `ItemRest`, `efa_utils`)
purify a *single* item pool at a time and leave the researcher to repeat the
process by hand across constructs, and to write up each step manually.

`efaTrail` automates both the multi-construct orchestration and the
audit-trail write-up.

## A minimal example

```{r setup}
library(efaTrail)

synthetic_reading <- read.csv(
  system.file("extdata", "synthetic_reading.csv", package = "efaTrail")
)

constructs <- list(
  SA = grep("^SA", names(synthetic_reading), value = TRUE),
  CS = grep("^CS", names(synthetic_reading), value = TRUE)
)

result <- efa_trail(synthetic_reading, constructs)
print(result)
```

## Inspecting the audit trail

```{r audit}
audit_report(result)
```

Each construct's `iterations` list records, at every step: the number of
items still in play, the overall KMO, the retained factor count, and which
item (if any) was removed and why -- exactly the information researchers
have traditionally compiled by hand.

```{r details}
str(result$SA$iterations[[1]], max.level = 1)
```

## Feeding the result into a CFA (lavaan)

Once a construct's item set is stable, `final_items` is ready to hand off
to `lavaan` for confirmatory factor analysis:

```{r lavaan, eval = FALSE}
library(lavaan)

model <- paste0("SA =~ ", paste(result$SA$final_items, collapse = " + "))
fit <- cfa(model, data = synthetic_reading)
summary(fit, fit.measures = TRUE, standardized = TRUE)
```
